Appendix

### 2019-06-24 manuscript/appendix.Rmd
add buffer composition category
explore trophic state breakdown by hu4

@@

g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
grid.draw(g)
```

>>>>

focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
                                             c("56", "57", "36", "37", "38")), 
                         stringsAsFactors = FALSE)

@@

g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
grid.draw(g)

test <- readRDS("../data/dt.rds") %>%
  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
  group_by(is_focal, trophic_state) %>%
  count() %>%
  tidyr::spread(trophic_state, n)
```

```{r predictor_maps}
# 
```
